factor_explorer

### 2014-06-22 ijlyttle/factor_explorer.Rmd

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      fill = input$fill_factor
    )  
  ) + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_fill_discrete(name = rct_labels()[["fill"]]) 
})
```

>>>>

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      fill = input$fill_factor
    )  
  ) + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_fill_brewer(type = "seq", name = rct_labels()[["fill"]]) 
})
```
